\documentclass{article}
\usepackage{bubblecv}
\usepackage{bibentry}
\usepackage[square, numbers, sort]{natbib}
% \usepackage{fontawesome5}



\begin{document}


\begin{cv}[avatar]{Felipe Inostroza Ferrari}{Robotics Engineer - Developer - Electrical Engineer, PhD.}


	\cvsection[summary]{Profile}  %-----------------------------------------------------------

	I'm a robotics engineer with a PhD in Electrical Engineering. My interests are Robotics, Autonomous Vehicles, robotic mapping and localization (SLAM) and sensor data processing in general.
	I am capable of designing and implementing robotic systems to solve real world applications. I can do work like choosing which sensors to use, or  writing the low level code required to process them, all the way to choosing which navigation algorithms to best control a mobile robot.

	My strong background in robotics has given me experience with writing and debugging code in C++, Python and ROS (both 1 and 2) as well as keeping track of it in Git.
	This experience has also allowed me to work with Linux and its multiple systems.
	Also as during my PhD I worked with an advisor who was a native English speaker, I was able to write my thesis in English and learned to communicate technical information efficiently in that language

	\cvsection[work]{Work Experience}  %------------------------------------------------------

	\begin{cvevent}[2019][present]
		\cvname{Research Associate}
		\cvdescription{Advanced Mining Technology Center (AMTC), Universidad de Chile}
		I currently work at AMTC in the University of Chile designing and developing mapping and localizations solutions for vehicles operating in underground mining as well as in autonomous navigation in general.
		From 2024 I have been the technical lead of the project of Automation of Load-Haul-Dump (LHD) vehicles.
	\end{cvevent}

	\begin{cvevent}[2025][present]
		\cvname{Part Time Professor}
		\cvdescription{Department of Electrical Engineering, Universidad de Chile}
		On the fall semester of 2025 I co-taught the course EL7009 - Mobile Robotics.
		In this course I taught, alongside professor Javier Ruiz-del-Solar, the basics of mobile robotics, sensing, motion planning and SLAM.
	\end{cvevent}


	\begin{cvevent}[2014][2021]
		\cvname{Auxiliary Teacher}
		\cvdescription{Department of Electrical Engineering, Universidad de Chile}
		I was tasked with making auxiliary classes, solving practical problems and guiding tutorials in the following courses
		\begin{itemize}
			\item Cumputational Inteligence and Robotics Laboratory (2014-2021),
			\item Robotics, Sensing and Autonomous Systems(2013-2019).
			\item System Control Fundamentals (2013-2014).
			\item Fault Diagnosis and Prognosis (2013-2013).
		\end{itemize}
	\end{cvevent}




	% \bibliographystyle{}
	%\bibliographystyle{IEEEtranN}
	\bibliographystyle{unsrtnat}



	\cvsidebar %-----------------------------------------------------------------------------


	\cvsection[contact]{Contact}  %----------------------------------------------------------

	\begin{cvitem}[Envelope][4]
		\textbf{Email}\\
		\href{mailto:pepeinostroza@gmail.com}{\texttt{pepeinostroza@gmail.com}}
	\end{cvitem}

	\cvseparator[3]
	\begin{cvitem}[Phone][4]
		\textbf{Phone}\\
		\href{tel:+56976499574}{\texttt{+56976499574}}
	\end{cvitem}

	\cvseparator[3]
	\begin{cvitem}[Home][4]
		\textbf{Home Address}\\
		Tucapel 233, depto. 2107, Ñuñoa\\ Santiago, Chile
	\end{cvitem}

	\cvseparator[3]
	\textbf{Social Media Links}\\
	\begin{cvitem}[][4]
		\href{https://https://github.com/finostro}{\faGithub \texttt{ Github}}
	\end{cvitem}
	\begin{cvitem}[][4]
		\href{https://www.researchgate.net/profile/Felipe-Inostroza-4}{\faResearchgate \texttt{ ResearchGate}}
	\end{cvitem}
	\begin{cvitem}[][4]
		\href{https://www.linkedin.com/in/felipe-inostroza-ferrari-a0852035/}{\faLinkedin \texttt{ LinkedIn}}
	\end{cvitem}

	\cvsection[skills]{Skills}  %-----------------------------------------------------------
	\cvskill{C++}{Advanced}{0.8}
	\cvskill{ROS/ROS2}{Advanced}{0.8}
	\cvskill{Python}{Intermediate}{0.6}
	\cvskill{Git}{Intermediate}{0.6}
	\cvseparator
	\begin{cvitem}
		Windows, Linux, Mac OS X
	\end{cvitem}

	\cvseparator

	\begin{cvitem}
		C, C++, Python, MATLAB, Git
	\end{cvitem}

	\cvseparator
	\begin{cvitem}
		Microsoft Office, Excel, OpenOffice, \LaTeX
	\end{cvitem}




	\cvsection[languages]{Languages}  %--------------------------------------------------------

	\cvskill{Spanish}{Native}{1.0}
	Spanish is my native language and I'm fluent in it.

	\cvskill{English}{Fluent}{0.9}
	English is my second language. I'm fluent in it and was recently tested with an 8.5/9 score on the IELTS academic test.

	\cvskill{German}{Basic}{0.1}
	I may be able to say a few words in German.









\end{cv}

\clearpage
\cvsection[education]{Education}  %------------------------------------------------------

\begin{cvevent}[2014][2023]
	\cvname{Doctorate in Electrical Engineering}
	\cvdescription{Department of Electrical Engineering, Universidad de Chile}
	My thesis topic was to apply modern Random Finite Sets (RFSs) theory to the problem of Simulatanous Localization and Mapping (SLAM). Modifications to existing state of the art algorithms were proposed and tested. Additionally, a new RFS-based algorithm was developed and tested with stereo cameras.
\end{cvevent}

\begin{cvevent}[2012][2014]
	\cvname{Master of Electrical Engineering}
	\cvdescription{Department of Electrical Engineering, Universidad de Chile}
	Two existing SLAM algorithm were modified and tested with 2D LIDAR data. The proposed modification was shown improve performance for both algorithms.
\end{cvevent}
\begin{cvevent}[2007][2014]
	\cvname{Electrical Engineering}
	\cvdescription{Department of Electrical Engineering, Universidad de Chile}
\end{cvevent}
\begin{cvevent}[2007][2014]
	\cvname{Primary and Secondary Education}
	\cvdescription{Colegio Alemán de Temuco}
\end{cvevent}
%\bibliography{references}
\nobibliography{../references}
\cvsection[publications]{Publications}
\begin{cvevent}
	\cvname{Journal Articles}
	\begin{itemize}
		\item \bibentry{inostroza_2024_jvsslam}
		\item \bibentry{inostroza_2023_robust_localization}
		\item \bibentry{cardenas_2023_autonomous_loading}
		\item \bibentry{inostroza2018modeling}
		\item \bibentry{leung2017chilean}
		\item \bibentry{leung2017relatingTSP}
		\item \bibentry{cola_metric_tro}
		\item \bibentry{glmbslam_sensors_Moratuwage}
		\item \bibentry{leung_2016_taes_multifeature}
	\end{itemize}
\end{cvevent}

\begin{cvevent}
	\cvname{Conference Papers}
	\begin{itemize}
		\item \bibentry{Leung2013}
		\item \bibentry{inostroza2014semantic}
		\item \bibentry{leung2014evaluating}
		\item \bibentry{inostroza2015incorporating}
		\item \bibentry{leung2015generalizing}
		\item \bibentry{glmb_slam_moratuwage}
		\item \bibentry{inostroza_fusion_2018_addressing}
		\item \bibentry{cola_metric_fusion_2015}
	\end{itemize}
\end{cvevent}

% \cvfootnote{
%     \tiny I agree to the processing of personal data provided in this document for realizing the recruitment process pursuant to the Personal Data Protection Act of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data and on the free movement of such data, and repealing Directive 95/46/EC (General Data Protection Regulation)
% }

\end{document}
